Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-07-10 rmd/manuscript.Rmd
Update manuscript.Rmd

**Figure 5** Relationships between the proportion of each patch state $\bar{\psi}$ (colors indicate different patch states) and ecosystem size under the chain motif scenario. Disturbance intensity is $\mu_m = 0.8$. The proportion of each patch state $\bar{\psi}$ is averaged over time for each simulation replicate. Lines indicate loess curves fitted to $500$ simulation replicates, and shades are associated 95% confidence intervals.Rows distinguish disturbance probability $p_m$, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

>>>>

**Figure 5** Relationships between the proportion of each patch state $\bar{\psi}$ (colors indicate different patch states) and ecosystem size under the chain motif scenario. Disturbance intensity is $\mu_m = 0.8$. The proportion of each patch state $\bar{\psi}$ is averaged over time for each simulation replicate. Lines indicate loess curves fitted to $500$ simulation replicates, and shades are associated 95% confidence intervals. Rows distinguish disturbance probability $p_m$, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.
